Minimizing post-shock forecasting error using disparate information

### 2020-08-05 manuscript/comp.tex
changes by deletion of covariates and revision by comments

% Created by tikzDevice version 0.12.3 on 2020-05-27 15:30:26
% !TEX encoding = UTF-8 Unicode
\documentclass[10pt]{article}
\usepackage{tikz}

@@

\begin{tikzpicture}[x=1pt,y=1pt]
\definecolor{fillColor}{RGB}{255,255,255}
\path[use as bounding box,fill=fillColor,fill opacity=0.00] (0,0) rectangle (578.16,289.08);
\begin{scope}
\path[clip] ( 48.00, 48.00) rectangle (554.16,277.08);
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 72.43,150.94) --
	( 75.27,164.79) --
	( 78.11,157.49) --
	( 80.95,165.92) --
	( 83.79,166.40) --
	( 86.63,141.84) --
	( 89.47,150.09) --
	( 92.31,143.93) --
	( 95.15,141.05) --
	( 97.99,145.70) --
	(100.83,139.65) --
	(103.67,178.59) --
	(106.51,163.76) --
	(109.35,143.77) --
	(112.19,137.72) --
	(115.03,164.14) --
	(117.87,143.58) --
	(120.71,166.91) --
	(123.55,163.52) --
	(126.40,145.84) --
	(129.24,155.56) --
	(132.08,140.91) --
	(134.92,146.00) --
	(137.76,155.61) --
	(140.60,151.70) --
	(143.44,158.08) --
	(146.28,157.50) --
	(149.12,162.02) --
	(151.96,166.12) --
	(154.80,159.26) --
	(157.64,149.45) --
	(160.48,145.98) --
	(163.32,156.42) --
	(166.16,141.35) --
	(169.00,146.25) --
	(171.84,165.79) --
	(174.68,133.16) --
	(177.52,164.74) --
	(180.36,158.63) --
	(183.20,174.39) --
	(186.04,136.64) --
	(188.88,142.35) --
	(191.72,165.33) --
	(194.56,177.10) --
	(197.41,169.75) --
	(200.25,166.95) --
	(203.09,116.51) --
	(205.93,139.49) --
	(208.77,140.86) --
	(211.61,181.44) --
	(214.45,157.88) --
	(217.29,160.28) --
	(220.13,161.32) --
	(222.97,174.87) --
	(225.81,148.01) --
	(228.65,118.11) --
	(231.49,167.94) --
	(234.33,167.87) --
	(237.17,178.18) --
	(240.01,165.32) --
	(242.85,151.88) --
	(245.69,151.67) --
	(248.53,151.92) --
	(251.37,128.89) --
	(254.21,159.78) --
	(257.05,144.18) --
	(259.89,155.47) --
	(262.73,164.76) --
	(265.57,152.05) --
	(268.42,138.91) --
	(271.26,143.64) --
	(274.10,141.06) --
	(276.94,166.61) --
	(279.78,177.14) --
	(282.62,143.52) --
	(285.46,129.06) --
	(288.30,134.98) --
	(291.14,126.11) --
	(293.98,179.60) --
	(296.82,162.55) --
	(299.66,178.83) --
	(302.50,133.78) --
	(305.34,124.87) --
	(308.18,142.06) --
	(311.02,157.78) --
	(313.86,132.62) --
	(316.70,148.93) --
	(319.54,130.16) --
	(322.38,152.67) --
	(325.22,156.53) --
	(328.06,145.81) --
	(330.90,145.85) --
	(333.74,164.04) --
	(336.59,162.10) --
	(339.43,137.37) --
	(342.27,177.60) --
	(345.11,138.08) --
	(347.95,158.99) --
	(350.79,145.39) --
	(353.63,165.05) --
	(356.47,136.95) --
	(359.31,166.26) --
	(362.15,151.18) --
	(364.99,143.86) --
	(367.83,154.91) --
	(370.67,151.74) --
	(373.51,154.30) --
	(376.35,126.88) --
	(379.19,135.58) --
	(382.03,152.86) --
	(384.87,171.42) --
	(387.71,136.46) --
	(390.55,130.68) --
	(393.39,141.79) --
	(396.23,146.31) --
	(399.07,119.63) --
	(401.91,132.99) --
	(404.75,143.78) --
	(407.60,169.91) --
	(410.44,180.48) --
	(413.28,132.66) --
	(416.12,158.14) --
	(418.96,163.74) --
	(421.80,167.20) --
	(424.64,169.82) --
	(427.48,208.40);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (578.16,289.08);
\definecolor{drawColor}{RGB}{0,0,0}

@@

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 48.00, 56.55) -- ( 48.00,265.51);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 48.00, 56.55) -- ( 42.00, 56.55);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 48.00, 86.40) -- ( 42.00, 86.40);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 48.00,116.25) -- ( 42.00,116.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 48.00,146.10) -- ( 42.00,146.10);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 48.00,175.96) -- ( 42.00,175.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 48.00,205.81) -- ( 42.00,205.81);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 48.00,235.66) -- ( 42.00,235.66);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 48.00,265.51) -- ( 42.00,265.51);

\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at ( 33.60, 56.55) {-6};

\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at ( 33.60, 86.40) {-4};

\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at ( 33.60,116.25) {-2};

\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at ( 33.60,146.10) {0};

\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at ( 33.60,175.96) {2};

\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at ( 33.60,205.81) {4};

\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at ( 33.60,235.66) {6};

\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at ( 33.60,265.51) {8};

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 48.00, 48.00) --
	(554.16, 48.00) --
	(554.16,277.08) --
	( 48.00,277.08) --
	( 48.00, 48.00);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (578.16,289.08);
\definecolor{drawColor}{RGB}{0,0,0}

@@

\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at (  9.60,162.54) {Response};
\end{scope}
\begin{scope}
\path[clip] ( 48.00, 48.00) rectangle (554.16,277.08);
\definecolor{drawColor}{RGB}{255,106,106}

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] ( 72.43,150.71) --
	( 75.27,152.99) --
	( 78.11,153.34) --
	( 80.95,153.46) --
	( 83.79,154.87) --
	( 86.63,154.01) --
	( 89.47,150.03) --
	( 92.31,152.38) --
	( 95.15,151.57) --
	( 97.99,152.37) --
	(100.83,152.36) --
	(103.67,150.86) --
	(106.51,156.31) --
	(109.35,153.24) --
	(112.19,151.49) --
	(115.03,151.36) --
	(117.87,153.65) --
	(120.71,151.38) --
	(123.55,152.92) --
	(126.40,153.78) --
	(129.24,151.96) --
	(132.08,152.95) --
	(134.92,151.02) --
	(137.76,151.57) --
	(140.60,152.69) --
	(143.44,152.68) --
	(146.28,153.09) --
	(149.12,152.91) --
	(151.96,153.40) --
	(154.80,153.72) --
	(157.64,154.05) --
	(160.48,150.47) --
	(163.32,151.15) --
	(166.16,154.68) --
	(169.00,150.91) --
	(171.84,152.67) --
	(174.68,154.71) --
	(177.52,150.54) --
	(180.36,152.87) --
	(183.20,154.34) --
	(186.04,155.31) --
	(188.88,151.72) --
	(191.72,150.98) --
	(194.56,153.67) --
	(197.41,154.62) --
	(200.25,153.87) --
	(203.09,154.64) --
	(205.93,147.78) --
	(208.77,151.29) --
	(211.61,149.62) --
	(214.45,154.76) --
	(217.29,154.96) --
	(220.13,152.57) --
	(222.97,154.38) --
	(225.81,154.97) --
	(228.65,151.07) --
	(231.49,147.57) --
	(234.33,153.88) --
	(237.17,154.51) --
	(240.01,156.10) --
	(242.85,153.60) --
	(245.69,152.48) --
	(248.53,152.70) --
	(251.37,150.55) --
	(254.21,150.42) --
	(257.05,153.27) --
	(259.89,150.70) --
	(262.73,154.55) --
	(265.57,152.18) --
	(268.42,153.01) --
	(271.26,149.72) --
	(274.10,153.84) --
	(276.94,151.75) --
	(279.78,152.74) --
	(282.62,153.59) --
	(285.46,151.51) --
	(288.30,150.68) --
	(291.14,149.01) --
	(293.98,151.89) --
	(296.82,154.30) --
	(299.66,153.42) --
	(302.50,155.56) --
	(305.34,151.16) --
	(308.18,147.57) --
	(311.02,152.92) --
	(313.86,151.71) --
	(316.70,150.02) --
	(319.54,152.22) --
	(322.38,150.09) --
	(325.22,153.11) --
	(328.06,152.16) --
	(330.90,151.37) --
	(333.74,150.41) --
	(336.59,154.30) --
	(339.43,152.44) --
	(342.27,151.58) --
	(345.11,154.49) --
	(347.95,149.53) --
	(350.79,154.05) --
	(353.63,151.10) --
	(356.47,153.07) --
	(359.31,150.01) --
	(362.15,155.43) --
	(364.99,152.12) --
	(367.83,150.94) --
	(370.67,152.10) --
	(373.51,151.70) --
	(376.35,154.23) --
	(379.19,148.51) --
	(382.03,151.49) --
	(384.87,151.86) --
	(387.71,153.13) --
	(390.55,150.34) --
	(393.39,150.97) --
	(396.23,151.09) --
	(399.07,151.14) --
	(401.91,148.35) --
	(404.75,150.18) --
	(407.60,150.74) --
	(410.44,154.68) --
	(413.28,156.36) --
	(416.12,149.02) --
	(418.96,152.85) --
	(421.80,153.32) --
	(424.64,153.53) --
	(427.48,154.47);
\definecolor{drawColor}{RGB}{255,0,255}

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 1pt off 3pt ,line join=round,line cap=round] ( 72.43,150.71) --
	( 75.27,152.99) --
	( 78.11,153.34) --
	( 80.95,153.46) --
	( 83.79,154.87) --
	( 86.63,154.01) --
	( 89.47,150.03) --
	( 92.31,152.38) --
	( 95.15,151.57) --
	( 97.99,152.37) --
	(100.83,152.36) --
	(103.67,150.86) --
	(106.51,156.31) --
	(109.35,153.24) --
	(112.19,151.49) --
	(115.03,151.36) --
	(117.87,153.65) --
	(120.71,151.38) --
	(123.55,152.92) --
	(126.40,153.78) --
	(129.24,151.96) --
	(132.08,152.95) --
	(134.92,151.02) --
	(137.76,151.57) --
	(140.60,152.69) --
	(143.44,152.68) --
	(146.28,153.09) --
	(149.12,152.91) --
	(151.96,153.40) --
	(154.80,153.72) --
	(157.64,154.05) --
	(160.48,150.47) --
	(163.32,151.15) --
	(166.16,154.68) --
	(169.00,150.91) --
	(171.84,152.67) --
	(174.68,154.71) --
	(177.52,150.54) --
	(180.36,152.87) --
	(183.20,154.34) --
	(186.04,155.31) --
	(188.88,151.72) --
	(191.72,150.98) --
	(194.56,153.67) --
	(197.41,154.62) --
	(200.25,153.87) --
	(203.09,154.64) --
	(205.93,147.78) --
	(208.77,151.29) --
	(211.61,149.62) --
	(214.45,154.76) --
	(217.29,154.96) --
	(220.13,152.57) --
	(222.97,154.38) --
	(225.81,154.97) --
	(228.65,151.07) --
	(231.49,147.57) --
	(234.33,153.88) --
	(237.17,154.51) --
	(240.01,156.10) --
	(242.85,153.60) --
	(245.69,152.48) --
	(248.53,152.70) --
	(251.37,150.55) --
	(254.21,150.42) --
	(257.05,153.27) --
	(259.89,150.70) --
	(262.73,154.55) --
	(265.57,152.18) --
	(268.42,153.01) --
	(271.26,149.72) --
	(274.10,153.84) --
	(276.94,151.75) --
	(279.78,152.74) --
	(282.62,153.59) --
	(285.46,151.51) --
	(288.30,150.68) --
	(291.14,149.01) --
	(293.98,151.89) --
	(296.82,154.30) --
	(299.66,153.42) --
	(302.50,155.56) --
	(305.34,151.16) --
	(308.18,147.57) --
	(311.02,152.92) --
	(313.86,151.71) --
	(316.70,150.02) --
	(319.54,152.22) --
	(322.38,150.09) --
	(325.22,153.11) --
	(328.06,152.16) --
	(330.90,151.37) --
	(333.74,150.41) --
	(336.59,154.30) --
	(339.43,152.44) --
	(342.27,151.58) --
	(345.11,154.49) --
	(347.95,149.53) --
	(350.79,154.05) --
	(353.63,151.10) --
	(356.47,153.07) --
	(359.31,150.01) --
	(362.15,155.43) --
	(364.99,152.12) --
	(367.83,150.94) --
	(370.67,152.10) --
	(373.51,151.70) --
	(376.35,154.23) --
	(379.19,148.51) --
	(382.03,151.49) --
	(384.87,151.86) --
	(387.71,153.13) --
	(390.55,150.34) --
	(393.39,150.97) --
	(396.23,151.09) --
	(399.07,151.14) --
	(401.91,148.35) --
	(404.75,150.18) --
	(407.60,150.74) --
	(410.44,154.68) --
	(413.28,156.36) --
	(416.12,149.02) --
	(418.96,152.85) --
	(421.80,153.32) --
	(424.64,153.53) --
	(427.48,232.35);
\definecolor{drawColor}{RGB}{0,191,255}

\path[draw=drawColor,line width= 0.8pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (424.64, 56.48) -- (424.64,268.60);
\definecolor{drawColor}{RGB}{255,0,255}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (421.80,198.87) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (421.80,225.04) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (421.80,209.87) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (421.80,235.83) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (421.80,199.87) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (421.80,243.89) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (421.80,238.37) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (421.80,227.80) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (421.80,215.99) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (421.80,198.98) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (421.80,231.17) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (421.80,206.34) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (421.80,237.93) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (421.80,243.74) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (421.80,219.73) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (421.80,229.69) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (421.80,211.53) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (421.80,242.97) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (421.80,222.68) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (421.80,201.98) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (421.80,241.35) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (421.80,215.35) circle (  2.25);

@@

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (421.80,221.46) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (421.80,219.17) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (421.80,216.79) circle (  2.25);

>>>>

% Created by tikzDevice version 0.12.3.1 on 2020-08-05 11:58:05
% !TEX encoding = UTF-8 Unicode
\documentclass[10pt]{article}
\usepackage{tikz}

@@

\begin{tikzpicture}[x=1pt,y=1pt]
\definecolor{fillColor}{RGB}{255,255,255}
\path[use as bounding box,fill=fillColor,fill opacity=0.00] (0,0) rectangle (578.16,252.94);
\begin{scope}
\path[clip] ( 48.00, 48.00) rectangle (554.16,240.94);
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 72.43,141.91) --
	( 75.27,148.65) --
	( 78.11,138.04) --
	( 80.95,120.32) --
	( 83.79,144.55) --
	( 86.63,128.04) --
	( 89.47,158.74) --
	( 92.31,142.28) --
	( 95.15,144.24) --
	( 97.99,150.16) --
	(100.83,129.86) --
	(103.67,156.20) --
	(106.51,161.19) --
	(109.35,150.66) --
	(112.19,143.27) --
	(115.03,126.88) --
	(117.87,118.05) --
	(120.71,139.15) --
	(123.55,135.40) --
	(126.40,140.74) --
	(129.24,149.36) --
	(132.08,115.48) --
	(134.92,139.71) --
	(137.76,114.03) --
	(140.60,125.67) --
	(143.44,139.07) --
	(146.28,144.69) --
	(149.12,130.89) --
	(151.96,140.09) --
	(154.80,126.64) --
	(157.64,111.23) --
	(160.48,121.82) --
	(163.32,149.80) --
	(166.16,149.85) --
	(169.00,139.78) --
	(171.84,158.01) --
	(174.68,141.87) --
	(177.52,133.42) --
	(180.36,131.05) --
	(183.20,129.40) --
	(186.04,142.69) --
	(188.88,144.63) --
	(191.72,130.06) --
	(194.56,121.56) --
	(197.41,118.55) --
	(200.25,119.73) --
	(203.09,140.14) --
	(205.93,137.20) --
	(208.77,125.79) --
	(211.61,150.02) --
	(214.45,134.16) --
	(217.29,137.62) --
	(220.13,143.96) --
	(222.97,145.02) --
	(225.81,137.14) --
	(228.65,147.61) --
	(231.49,162.41) --
	(234.33,138.41) --
	(237.17,162.38) --
	(240.01,127.19) --
	(242.85,125.12) --
	(245.69,134.60) --
	(248.53,134.89) --
	(251.37,158.83) --
	(254.21,122.69) --
	(257.05,117.16) --
	(259.89,147.80) --
	(262.73,138.62) --
	(265.57,123.35) --
	(268.42,140.39) --
	(271.26,137.29) --
	(274.10,148.46) --
	(276.94,135.80) --
	(279.78,134.54) --
	(282.62,139.54) --
	(285.46,143.03) --
	(288.30,143.37) --
	(291.14,107.15) --
	(293.98,121.09) --
	(296.82,144.70) --
	(299.66,143.32) --
	(302.50,149.80) --
	(305.34,113.62) --
	(308.18,139.96) --
	(311.02,134.15) --
	(313.86,130.85) --
	(316.70,135.42) --
	(319.54,131.11) --
	(322.38,145.18) --
	(325.22,143.55) --
	(328.06,141.15) --
	(330.90,125.31) --
	(333.74,129.29) --
	(336.59,118.52) --
	(339.43,146.06) --
	(342.27,140.93) --
	(345.11,151.97) --
	(347.95,136.60) --
	(350.79,114.01) --
	(353.63,120.33) --
	(356.47,142.22) --
	(359.31,130.73) --
	(362.15,138.80) --
	(364.99,114.92) --
	(367.83,152.60) --
	(370.67,139.26) --
	(373.51,137.13) --
	(376.35,140.56) --
	(379.19,149.07) --
	(382.03,151.38) --
	(384.87,153.12) --
	(387.71,126.88) --
	(390.55,137.55) --
	(393.39,137.71) --
	(396.23,129.83) --
	(399.07,123.04) --
	(401.91,117.89) --
	(404.75,132.35) --
	(407.60,141.10) --
	(410.44,137.00) --
	(413.28,143.73) --
	(416.12,131.05) --
	(418.96,129.54) --
	(421.80,129.16) --
	(424.64,128.38) --
	(427.48,164.19);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (578.16,252.94);
\definecolor{drawColor}{RGB}{0,0,0}

@@

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 48.00, 67.43) -- ( 48.00,190.54);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 48.00, 67.43) -- ( 42.00, 67.43);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 48.00,128.99) -- ( 42.00,128.99);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 48.00,190.54) -- ( 42.00,190.54);

\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at ( 33.60, 67.43) {-5};

\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at ( 33.60,128.99) {0};

\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at ( 33.60,190.54) {5};

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 48.00, 48.00) --
	(554.16, 48.00) --
	(554.16,240.94) --
	( 48.00,240.94) --
	( 48.00, 48.00);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (578.16,252.94);
\definecolor{drawColor}{RGB}{0,0,0}

@@

\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at (  9.60,144.47) {Response};
\end{scope}
\begin{scope}
\path[clip] ( 48.00, 48.00) rectangle (554.16,240.94);
\definecolor{drawColor}{RGB}{255,106,106}

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] ( 72.43,137.81) --
	( 75.27,136.65) --
	( 78.11,143.49) --
	( 80.95,137.43) --
	( 83.79,130.64) --
	( 86.63,140.10) --
	( 89.47,133.95) --
	( 92.31,138.95) --
	( 95.15,138.13) --
	( 97.99,134.38) --
	(100.83,138.70) --
	(103.67,136.65) --
	(106.51,142.33) --
	(109.35,140.08) --
	(112.19,140.76) --
	(115.03,135.30) --
	(117.87,131.53) --
	(120.71,134.31) --
	(123.55,136.31) --
	(126.40,138.07) --
	(129.24,138.68) --
	(132.08,133.35) --
	(134.92,135.06) --
	(137.76,137.42) --
	(140.60,132.08) --
	(143.44,134.84) --
	(146.28,141.15) --
	(149.12,136.50) --
	(151.96,137.75) --
	(154.80,136.26) --
	(157.64,132.36) --
	(160.48,135.15) --
	(163.32,133.44) --
	(166.16,135.02) --
	(169.00,137.46) --
	(171.84,137.44) --
	(174.68,138.85) --
	(177.52,137.64) --
	(180.36,136.64) --
	(183.20,136.98) --
	(186.04,135.19) --
	(188.88,135.00) --
	(191.72,137.46) --
	(194.56,133.62) --
	(197.41,136.58) --
	(200.25,133.35) --
	(203.09,137.85) --
	(205.93,138.76) --
	(208.77,132.56) --
	(211.61,136.25) --
	(214.45,135.48) --
	(217.29,136.00) --
	(220.13,134.15) --
	(222.97,138.92) --
	(225.81,140.34) --
	(228.65,137.72) --
	(231.49,138.74) --
	(234.33,140.75) --
	(237.17,137.08) --
	(240.01,139.13) --
	(242.85,132.23) --
	(245.69,135.17) --
	(248.53,135.31) --
	(251.37,134.56) --
	(254.21,137.20) --
	(257.05,135.96) --
	(259.89,133.73) --
	(262.73,140.13) --
	(265.57,133.33) --
	(268.42,134.06) --
	(271.26,136.71) --
	(274.10,138.64) --
	(276.94,143.32) --
	(279.78,136.35) --
	(282.62,136.03) --
	(285.46,138.94) --
	(288.30,139.04) --
	(291.14,138.48) --
	(293.98,133.60) --
	(296.82,137.06) --
	(299.66,135.32) --
	(302.50,136.59) --
	(305.34,139.19) --
	(308.18,132.33) --
	(311.02,130.50) --
	(313.86,133.96) --
	(316.70,137.48) --
	(319.54,136.37) --
	(322.38,135.54) --
	(325.22,141.95) --
	(328.06,137.28) --
	(330.90,136.24) --
	(333.74,135.82) --
	(336.59,129.34) --
	(339.43,131.63) --
	(342.27,137.63) --
	(345.11,139.18) --
	(347.95,141.59) --
	(350.79,135.78) --
	(353.63,132.71) --
	(356.47,132.87) --
	(359.31,137.75) --
	(362.15,135.79) --
	(364.99,140.06) --
	(367.83,133.34) --
	(370.67,138.30) --
	(373.51,137.87) --
	(376.35,138.13) --
	(379.19,134.63) --
	(382.03,136.24) --
	(384.87,143.24) --
	(387.71,134.81) --
	(390.55,133.80) --
	(393.39,135.75) --
	(396.23,137.51) --
	(399.07,135.80) --
	(401.91,130.45) --
	(404.75,132.80) --
	(407.60,136.90) --
	(410.44,137.73) --
	(413.28,138.35) --
	(416.12,138.71) --
	(418.96,134.35) --
	(421.80,137.02) --
	(424.64,137.94) --
	(427.48,134.70);
\definecolor{drawColor}{RGB}{255,0,255}

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 1pt off 3pt ,line join=round,line cap=round] ( 72.43,137.81) --
	( 75.27,136.65) --
	( 78.11,143.49) --
	( 80.95,137.43) --
	( 83.79,130.64) --
	( 86.63,140.10) --
	( 89.47,133.95) --
	( 92.31,138.95) --
	( 95.15,138.13) --
	( 97.99,134.38) --
	(100.83,138.70) --
	(103.67,136.65) --
	(106.51,142.33) --
	(109.35,140.08) --
	(112.19,140.76) --
	(115.03,135.30) --
	(117.87,131.53) --
	(120.71,134.31) --
	(123.55,136.31) --
	(126.40,138.07) --
	(129.24,138.68) --
	(132.08,133.35) --
	(134.92,135.06) --
	(137.76,137.42) --
	(140.60,132.08) --
	(143.44,134.84) --
	(146.28,141.15) --
	(149.12,136.50) --
	(151.96,137.75) --
	(154.80,136.26) --
	(157.64,132.36) --
	(160.48,135.15) --
	(163.32,133.44) --
	(166.16,135.02) --
	(169.00,137.46) --
	(171.84,137.44) --
	(174.68,138.85) --
	(177.52,137.64) --
	(180.36,136.64) --
	(183.20,136.98) --
	(186.04,135.19) --
	(188.88,135.00) --
	(191.72,137.46) --
	(194.56,133.62) --
	(197.41,136.58) --
	(200.25,133.35) --
	(203.09,137.85) --
	(205.93,138.76) --
	(208.77,132.56) --
	(211.61,136.25) --
	(214.45,135.48) --
	(217.29,136.00) --
	(220.13,134.15) --
	(222.97,138.92) --
	(225.81,140.34) --
	(228.65,137.72) --
	(231.49,138.74) --
	(234.33,140.75) --
	(237.17,137.08) --
	(240.01,139.13) --
	(242.85,132.23) --
	(245.69,135.17) --
	(248.53,135.31) --
	(251.37,134.56) --
	(254.21,137.20) --
	(257.05,135.96) --
	(259.89,133.73) --
	(262.73,140.13) --
	(265.57,133.33) --
	(268.42,134.06) --
	(271.26,136.71) --
	(274.10,138.64) --
	(276.94,143.32) --
	(279.78,136.35) --
	(282.62,136.03) --
	(285.46,138.94) --
	(288.30,139.04) --
	(291.14,138.48) --
	(293.98,133.60) --
	(296.82,137.06) --
	(299.66,135.32) --
	(302.50,136.59) --
	(305.34,139.19) --
	(308.18,132.33) --
	(311.02,130.50) --
	(313.86,133.96) --
	(316.70,137.48) --
	(319.54,136.37) --
	(322.38,135.54) --
	(325.22,141.95) --
	(328.06,137.28) --
	(330.90,136.24) --
	(333.74,135.82) --
	(336.59,129.34) --
	(339.43,131.63) --
	(342.27,137.63) --
	(345.11,139.18) --
	(347.95,141.59) --
	(350.79,135.78) --
	(353.63,132.71) --
	(356.47,132.87) --
	(359.31,137.75) --
	(362.15,135.79) --
	(364.99,140.06) --
	(367.83,133.34) --
	(370.67,138.30) --
	(373.51,137.87) --
	(376.35,138.13) --
	(379.19,134.63) --
	(382.03,136.24) --
	(384.87,143.24) --
	(387.71,134.81) --
	(390.55,133.80) --
	(393.39,135.75) --
	(396.23,137.51) --
	(399.07,135.80) --
	(401.91,130.45) --
	(404.75,132.80) --
	(407.60,136.90) --
	(410.44,137.73) --
	(413.28,138.35) --
	(416.12,138.71) --
	(418.96,134.35) --
	(421.80,137.02) --
	(424.64,137.94) --
	(427.48,198.96);
\definecolor{drawColor}{RGB}{0,191,255}

\path[draw=drawColor,line width= 0.8pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (424.64, 55.15) -- (424.64,233.80);
\definecolor{drawColor}{RGB}{255,0,255}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (421.80,189.66) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (421.80,212.78) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (421.80,176.65) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (421.80,201.49) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (421.80,198.71) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (421.80,181.04) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (421.80,229.00) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (421.80,206.56) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (421.80,197.52) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (421.80,206.18) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (421.80,187.44) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (421.80,197.65) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (421.80,209.44) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (421.80,197.73) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (421.80,187.08) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (421.80,203.49) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (421.80,166.81) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (421.80,196.41) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (421.80,183.27) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (421.80,165.90) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (421.80,179.34) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (421.80,169.71) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (421.80,233.80) circle (  2.25);

@@

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (421.80,201.56) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (421.80,163.02) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (421.80,207.09) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (421.80,188.70) circle (  2.25);
